Selection of Polynomial Features by Genetic Algorithms

### 2013-10-30 texts/submission_02-asc/paper_spfga-review.tex
- Second Journal - Added paywalled journals

%
%	ACRONYMS
%
\usepackage{acronym}
\acrodef{GA}{Genetic algorithms}
\acrodef{rmse}[error]{root-mean-square error}
\acrodef{GAPoly}[\textsc{GAPoly}]{Genetic Algorithms for Polynomials}
%

@@

The proposed method has competitive results comparing with some well-known regression methods. Only Random Forest outperforms \ac{GAPoly} systematically (it also outperforms all the other regression algorithms). One exception --- besides the artificial dataset that uses a straightforward polynomial relation --- is the Auto MPG dataset where \ac{GAPoly} has comparable results. This is evidence that applying standard genetic operators for polynomial model searching is a viable tool for regression purposes.

>>>>

%
%	ACRONYMS
%
\usepackage{acronym}
%
\acrodef{GA}{Genetic algorithms}
\acrodef{rmse}[error]{root-mean-square error}
\acrodef{GAPoly}[\textsc{GAPoly}]{Genetic Algorithms for Polynomials}
%

@@

Of all the non-ensemble regression methods considered, the proposed method is the one that shows, with one exception, the lowest error. Only Random Forest outperforms \ac{GAPoly} systematically (it also outperforms all the other regression algorithms). The single non-ensemble exception --- besides the artificial dataset that uses a straightforward polynomial relation --- is the Auto MPG dataset where \ac{GAPoly} has comparable results. This is evidence that applying standard genetic operators for polynomial model searching is a viable tool for regression purposes.
